Msc Thesis Figures

### 2020-08-20 docs/msc_thesis_figures.Rmd
udpates

results_clean <- read_rds("../outputs/final/stsim_run_results.csv") %>% 
  dplyr::select(scenarioId, name) %>% 
  mutate(name =  gsub(.$name, pattern = " \\(.+\\)", replacement = "")) %>% 
  mutate(sce =  paste0("sce_", .$scenarioId)) %>% 
  mutate(chapter = c("none", rep("both", 3), rep("chap_1", 3), rep("chap_2", 9))) %>% 
  mutate(splitted = str_split(name, " \\| ")) %>% 
  mutate(climate = unlist(map(splitted, ~unlist(.x[2])))) %>% 
  mutate(run = unlist(map(splitted, ~unlist(.x[1])))) %>% 
  dplyr::select(-splitted) %>% 
  replace_na(list(climate = "none")) %>% 
  mutate(code = c("Control", sce_code_vec)) %>% 
  mutate(code_run = c("control", sce_code_vec_run))

# Final extracted datasets
df_final <- readRDS("../outputs/final/final_df_current_density.csv") %>%
  mutate(timestep = (timestep*10)+1990, source = "model")
df_final_origin <- readRDS("../outputs/final/final_df_origin_current_density.csv") %>%
  mutate(timestep = timestep*10+1990, source = "model")

>>>>

results_clean <- read_csv("../outputs/final/stsim_run_results.csv") %>% 
  dplyr::select(scenarioId, name) %>% 
  mutate(name =  gsub(.$name, pattern = " \\(.+\\)", replacement = "")) %>% 
  mutate(sce =  paste0("sce_", .$scenarioId)) %>% 
  mutate(chapter = c("none", rep("both", 3), rep("chap_1", 3), rep("chap_2", 9))) %>% 
  mutate(splitted = str_split(name, " \\| ")) %>% 
  mutate(climate = unlist(map(splitted, ~unlist(.x[2])))) %>% 
  mutate(run = unlist(map(splitted, ~unlist(.x[1])))) %>% 
  dplyr::select(-splitted) %>% 
  replace_na(list(climate = "none")) %>% 
  mutate(code = c("Control", sce_code_vec)) %>% 
  mutate(code_run = c("control", sce_code_vec_run))

# Final extracted datasets
df_final <- read_csv("../outputs/final/final_df_current_density.csv") %>%
  mutate(timestep = (timestep*10)+1990, source = "model")
df_final_origin <- read_csv("../outputs/final/final_df_origin_current_density.csv") %>%
  mutate(timestep = timestep*10+1990, source = "model")
